---
title: "R Notebook"
output: html_notebook
---

 

```{r}
## poisson regression
poem <- read.csv("//Users/jianingyi/Documents/Documents - Jenny Yi’s MacBook Air/mssp/ma676/consulting/MA677_Poem_project/poem_project.csv")
poem$end <- as.factor(poem$end )
poem$followed <- as.factor(poem$followed )
poem$poem6 <- as.factor(poem$poem6 )

model0 <- glm(count ~ poem2+poem3+poem4+poem5+poem6+end+followed, family = poisson, data = poem)
model1 <- glm(count ~ poem2+poem3+poem4+poem5+poem6+end+followed+poem6:end+poem6:followed, family = poisson, data = poem)
```


```{r}
model0_summary <- summary(model0)

# 获取coefficients矩阵的行名
coefficient_names <- rownames(model0_summary$coefficients)

# 替换行名以反映新的标签
coefficient_names <- sub("^followed$", "Followed by Nothing", coefficient_names)
coefficient_names <- sub("followed1", "Followed by Vowel", coefficient_names)
coefficient_names <- sub("followed2", "Followed by Consonant", coefficient_names)
coefficient_names <- sub("^end$", "End with As", coefficient_names)
coefficient_names <- sub("end1", "End with Ous", coefficient_names)

# 重新赋值coefficients矩阵的行名
rownames(model0_summary$coefficients) <- coefficient_names

# 打印修改后的summary对象
print(model0_summary)
```


```{r}
model1_summary <- summary(model1)

# 获取coefficients矩阵的行名
coefficient_names <- rownames(model1_summary$coefficients)
coefficient_names <- sub("followed1", "Followed by Vowel", coefficient_names)
coefficient_names <- sub("followed2", "Followed by Consonant", coefficient_names)
coefficient_names <- sub("poem61:followed1", "Poem6 & Followed by Vowel", coefficient_names)
coefficient_names <- sub("poem61:followed2", "Poem6 & Followed by Consonant", coefficient_names)

# 对于end变量的更改
coefficient_names <- sub("end1", "End with Ous", coefficient_names)

# 如果还有end和poem6的交互项也需要改名
coefficient_names <- sub("poem61:end1", "Poem6 & End with Ous", coefficient_names)

# 重新赋值coefficients矩阵的行名
rownames(model1_summary$coefficients) <- coefficient_names

# 打印修改后的summary对象
print(model1_summary)
```


```{r}
## likelyhood ratio test
lrt_result <- anova(model0, model1, test="Chisq")
lrt_result
```
```{r}
par(mfrow=c(1,2)) 
plot(model0, which=1) 
abline(h=0, col="red") 
title(main="Residuals vs Fitted for model")

plot(model1, which=1) 
abline(h=0, col="red") 
title(main="Residuals vs Fitted for model2")
```


```{r}
# binned residual plots
library(arm)
old.par <- par(no.readonly = TRUE)
x <- predict(model)
 y <- resid(model)
 binnedplot(x,y)
par(old.par)
x <- predict(model2)
y <- resid(model2)
binnedplot(x,y)
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

